---
title: "HW5"
output: html_document
date: "2025-04-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## head(house_prices)

library(ggplot2)

'''

prompt : create a faceted line plot using ggplot2 to show the trend of

house_price_index over the years for each state with cusom ticks on the x axis

80 for 1980, 00 for 2000 and 20 for 2020

'''

ggplot(house_prices, aes(x = date, y = house_price_index)) +

geom_line() +

facet_wrap(\~ state) +

scale_x_continuous(breaks = c(1980, 2000, 2020),

labels = c("’80", "’00", "’20")) +

labs(x = "Year", y = "House Price Index",

title = "Trends in House Price Index by State (1980–2020)") +

theme_minimal()

'''

prompt : use gather() from tidyr to reshape the data ub a way that it will have

measure and value columns for house_price_index and unemploy_perc, respectively,

in two columns. You should leave out remaining attributes by using ”-” in front

them inside the function. Then, direct the output to a new data frame called

house_reshaped

'''

library(tidyr)

house_reshaped \<- gather(house_prices,

key = "measure",

value = "value",

-date,

-state)

ggplot(house_prices, aes(x = date, y = house_price_index)) +

geom_line() +

facet_wrap(\~ state) +

scale_x_continuous(breaks = c(1980, 2000, 2020),

labels = c("’80", "’00", "’20")) +

labs(x = "Year", y = "House Price Index",

title = "Trends in House Price Index by State (1980–2020)") +

theme_minimal()

```{r}
head(house_prices)

library(ggplot2)



ggplot(house_prices, aes(x = date, y = house_price_index)) +
  geom_line() +
  facet_wrap(~ state) +
  scale_x_continuous(breaks = c(1980, 2000, 2020),
                     labels = c("’80", "’00", "’20")) +
  labs(x = "Year", y = "House Price Index",
       title = "Trends in House Price Index by State (1980–2020)") +
  theme_minimal()



library(tidyr)

house_reshaped <- gather(house_prices,
                         key = "measure", 
                         value = "value", 
                         -date, 
                         -state)

ggplot(house_prices, aes(x = date, y = house_price_index)) +
  geom_line() +
  facet_wrap(~ state) +
  scale_x_continuous(breaks = c(1980, 2000, 2020),
                     labels = c("’80", "’00", "’20")) +
  labs(x = "Year", y = "House Price Index",
       title = "Trends in House Price Index by State (1980–2020)") +
  theme_minimal()

```
